\chapter{\uppercase{Background}}\label{Ch:Background}
This chapter gives background knowledge as regards the Arabic Poetry and Al-Arud study rules and details. It also contains basic knowledge of Deep Learning concepts with a Literature Review of the previous work in this problem area. 

Each Arabic letter represents a consonant, which means that short vowels are not represented by the 36 characters; for this
reason, the need for diacritics arises. Diacritics are symbols that come after a letter to state the short vowel accompanied by that letter. There are four diacritics \textarabic{◌َ} \textarabic{◌ُ}
\textarabic{◌ِ} \textarabic{◌ْ} which represent the following short vowels /\textit{a}/, /\textit{u}/, /\textit{i}/ and \textit{no-vowel} respectively; their names are \textit{fat-ha, dam-ma, kas-ra and sukun} respectively. The first three symbols are called \textit{harakat}. Table~\ref{Tab:Diacritics_Dal} shows the 4 diacritics on a letter.
There are two more sub-diacritics made up of the basic four to represent two cases: \textit{Shadaa} and \textit{Tanween}.%

\begin{definition}\label{def:shadaa_definition}
  \textbf{\textit{Shadaa}}  \hfill \\
To indicate the letter is doubled. Any letter with shaddah (\textarabic{ ّ }) should be duplicated: the first letter with a constant \textit{(sukun)} and second letter with a vowel \textit{(haraka)}~\cite{Alnagdawi2013FindingArabicPoemMeter}; Table~\ref{Tab:Diacritics_Dal} shows the \textit{dal} with \textit{shadda} and the original letters. %
%
\end{definition}
\begin{definition}\label{def:tanween_definition}
  \textbf{\textit{Tanween}} \hfill \\
  This doubles the short vowel, and can convert \textit{Tanween fathah}, \textit{Tanween dhammah} or \textit{Tanween kasrah} by replacing it with the appropriate vowel (\textarabic{◌ُ} – dhammah, \textarabic{◌َ} – fathah or \textarabic{◌ِ} –kasrah ) then adding the \textit{Noon} letter with consonant to the end of the word~\cite{Alnagdawi2013FindingArabicPoemMeter}. Table~\ref{Tab:Tanween_Dal} shows the difference between the original letter and the letter with \textit{Tanween}
  
\end{definition}%


\begin{table}[h]
  \centering
  \begin{tabular}{c c c c c c c c}
    % \hline
    \toprule
    \textbf{\small{Diacritics}}     & \small{\textit{without}} & \small{\textit{fat-ha}} &
                                                                                           \small{\textit{kas-ra}} & \small{\textit{dam-ma}} & \small{\textit{sukun}} & \small{\textit{letter with Shadda }} & \small{\textit{letters without shadaa  }} \\
                                                                                           % \hline
    \midrule
    \textbf{\small{Shape}}   & \textarabic{د} & \textarabic{دَ} & \textarabic{دِ} &
                                                                                  \textarabic{دُ} & \textarabic{دْ}  & \textarabic{دَّ} &  \textarabic{دْدَ}\\
                                                                                  % \hline
    \bottomrule
  \end{tabular}
  \caption{Diacritics on the letter  \textarabic{ د }}\label{Tab:Diacritics_Dal}
\end{table}
\begin{table}[h]
  \centering
  \begin{tabular}{c c c}
    % \hline
    \toprule
    \textbf{\small{Diacritics}} & \small{\textit{letter with tanween }} & \small{\textit{letters without tanween}} \\
    % \hline
    \midrule
    \textbf{\small{Tanween Fat-ha}}  & \textarabic{دً} &  \textarabic{دَ+نْ}\\
    \textbf{\small{Tanween Dam-ma}}  & \textarabic{دٌ} &  \textarabic{دُ+نْ}\\
    \textbf{\small{Tanween Kas-ra}}  & \textarabic{دٍ} &  \textarabic{دِ+نْ}\\
    \bottomrule
  \end{tabular}
  \caption{Tanween diacritics on the letter  \textarabic{ د }} \label{Tab:Tanween_Dal}
\end{table}%

% \clearpage
% table: dal with diacritics

Arabs pronounce the sound \textit{/n/} accompanied \textit{Sukun} at the end the indefinite words; that sound corresponds to this letter \textarabic{نْ}, and is called \textit{noon-Sakinah}. However, it is just a phone, not a part of the indefinite word; if a word comes as a definite word, no additional sound is added. Since it is not an essential sound, it is not written as a letter, but is written as \textit{tanween} \textarabic{◌ٌ ◌ً ◌ٍ}. \textit{Tanween} states the sound \textit{noon-Sakinah}, but as you have noticed, there are 3 \textit{tanween} symbols. This is because  \textit{tanween} is added as a diacritic over the last letter of the indefinite word; one of the 3 \textit{harakat} accompanies the last letter, the last letter's \textit{haraka} needs to be stated in addition to the sound \textit{noon-Sakinah}, so \textit{tanween} doubles the last letter's \textit{haraka}.In this way, the last letter's \textit{haraka} is preserved, in addition to stating the sound \textit{noon-Sakinah}; for example, \textarabic{رَجُلُ + نْ} is written
\textarabic{رَجُلٌ} and  \textarabic{رَجُلِ + نْ} is written \textarabic{رَجُلٍ}

Those two definitions. Definition ~\ref{def:shadaa_definition} and
Definition~\ref{def:tanween_definition} help us to reduce the dimension of the letter’s feature vector, as we will see in the \textit{preparing data} section. Diacritics make short vowels clearer, but are not necessary. Moreover, a phrase without full diacritics or with just some on some letters is right linguistically, so it is permissible to drop them from the text. In Unicode, Arabic diacritics are standalone symbols, each of which has its own unicode. This is in contrast to the Latin diacritics; e.g., in the set \textit{\{ê, é, è, ë, ē, ĕ,
  ě\}}, each combination of the letter \textit{e} and a diacritic is represented by one unicode.

\begin{table}[h]
  \centering
\begin{tabular}{c c c c c c c c c}
    % \hline
    \toprule
    \textbf{\small{Indices}} & \multicolumn{8}{c}{\textbf{\small{Letters}}} \\
                                                                                           % \hline
    \midrule
    \textbf{\small{1:8}}   & \textarabic{ا} & \textarabic{ب} & \textarabic{ت} &\textarabic{ث} & \textarabic{ج}  & \textarabic{ح} &  \textarabic{خ}  &  \textarabic{د}\\
    \textbf{\small{9:16}}   & \textarabic{ذ} & \textarabic{ر} & \textarabic{ز} &\textarabic{س} & \textarabic{ش}  & \textarabic{ص} &  \textarabic{ض}  & \textarabic{ط}\\                                                                                  %
    \textbf{\small{17:24}}   & \textarabic{ظ} & \textarabic{ع} & \textarabic{غ} &\textarabic{ف} & \textarabic{ق}  & \textarabic{ك} &  \textarabic{ل}  & \textarabic{م}\\                                                                                  %
    \textbf{\small{25:32}}   & \textarabic{ن} & \textarabic{ـه} & \textarabic{و} &\textarabic{ي} & \textarabic{ء}  & \textarabic{آ} &  \textarabic{أ}  & \textarabic{ؤ}\\                                                                                  %
            \textbf{\small{33:36}}   & \textarabic{إ} & \textarabic{ئ} & \textarabic{ى} &  \textarabic{ة} &   &  &   & \\
    \bottomrule
              \end{tabular}
  \caption{Arabic Letters used in our research}\label{Tab:Arabic_Letters}
\end{table}


%\clearpage

\input{./chapters/sec_background_arud_science}

\clearpage

\input{./chapters/sec_background_deep_learning}

\clearpage




%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../master"
%%% TeX-engine: xetex
%%% End:
