\addcontentsline{toc}{chapter}{References}
\makeatletter
\renewcommand{\ps@plain}{%
\renewcommand\@oddhead{\hfil\normalfont\textrm{\thepage}}%
\renewcommand\@evenhead{}%
\renewcommand\@oddfoot{}%
\renewcommand\@evenfoot{}%
}
\makeatother
\pagestyle{myheadings}
\renewcommand\bibname{\uppercase{References}}
\begin{thebibliography}{300}
\bibitem{stat} THOMAS A. CIULLA, ARMANDO G. AMADOR, BERNARD ZINMAN, "Diabetic Retinopathy and Diabetic Macular Edema," DIABETES CARE, VOL. 26, NO. 9, SEPTEMBER 2003.
\bibitem{g} "Classification of Diabetic Retinopathy from Fluorescein Angiograms," Journal OPTHALMOLOGY, vol. 98, 1991.
\bibitem{quant} R. Theodore Smith, Carol M. Lee, Howard C. Charles, Marilyn Farber, and Jose G. Cunha-Vaz, "Quantification of Diabetic Macular Edema," Arch Opthalmol, VOL. 105, Feb. 1987.
\bibitem{FA} S. Dithmar and F. G. Holz 2008. Fluorescence Angiography in Opthalmology. Springer.
\bibitem{retinaloc} Frank ter Haar, "Automatic localization of the optic disc in digital colour images of the human retina," Master Thesis, Utrecht University, December 2005.
\bibitem{webr} www.vitrualmedicalcentre.com
\bibitem{book} Elia Duh 2008. Diabetic Retinopathy. Humana Press, Totowa, USA.
\bibitem{book2} G. E. Lang 2007. Diabetic Retinopathy. Karger, Switzerland.

%registration

\bibitem{survey2} Lisa Gottesfeld Brwon, "A survey of Image Registration techniques," ACM
Computing Surveys VOL. 24, pp.  326$-$376, 1992.% {survey}
\bibitem{ziv} Min Xu, Hao Chen, and Pramod K. Varshney, "Ziv$-$Zakai Bounds on Image Registration," IEEE TRANSACTIONS ON SIGNAL PROCESSING, VOL. 57, NO. 5, MAY 2009.
%Phase-Based
\bibitem{Phase1} Hassan Foroosh (Shekarforoush), Josiane B. Zerubia, and Marc Berthod, "Extension of Phase Correlation to Subpixel Registration," IEEE TRANSACTIONS ON INFORMATION TECHNOLOGY IN BIOMEDICINE, VOL. 10, NO. 1, JANUARY 2006. %Not retina\ area-phase corre
\bibitem{Phase2} Georgios Tzimiropoulos, Vasileios Argyriou, Stefanos Zafeiriou, and Tania Stathaki, "Robust FFT-Based Scale-Invariant Image Registration with Image Gradients," IEEE TRANSACTIONS ON PATTERN ANALYSIS AND MACHINE INTELLIGENCE, VOL. 32, 2010.%area-phase corre
\%bibitem{survey} Barbara Zitova, and Jan Flusser, "Image registration methods: a survey," Image and Vision Computing VOL. 21, pp. 977$-$1000, 2003.%
%Feature-Based
\bibitem{Control} W. E. Hart and M. H. Goldbaum, "Registering retinal images using automatically selected control point pairs," in Proc. IEEE Int. Conf. Image Processing, VOL. 3, pp. 576$-$580, Nov. 1994.%feature-correlation/affine/least squares for assessment
\bibitem{Montage} Douglas E. Becker, Ali Can, James N. Turner, Howard L. Tanenbaum, and Badrinath Roysam, "Image Processing Algorithms for Retinal Montage Synthesis, Mapping, and Real-Time Location Determination," IEEE TRANSACTIONS ON BIOMEDICAL ENGINEERING, VOL. 45, NO. 1, JANUARY 1998.%feature/The similarity between two histograms is then calculated by a sum-of-squared-difference
\bibitem{Hough} F. Zana and J. C. Klein, "A Multimodal Registration Algorithm of Eye Fundus Images Using Vessels Detection and Hough Transform," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 18, NO. 5, MAY 1999.%feature-based/affine/fluorescein with color/
\bibitem{Creases} D. Lloret, J. Serrat, A. M. Lopez, A. Soler, and J. J. Villaneuva, "Retinal image registration using creases as anatomical landmarks," in IEEE Proc. Int. Conf. Pattern Recognition, VOL. 3, pp. 203$-$206, Sep. 2000. %feature/correlation/{Mutimodal}
\bibitem{MultiRes} Philippe Thévenaz, and Michael Unser, "Optimization of Mutual Information for Multiresolution Image Registration," IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 9, NO. 12, DECEMBER 2000.%optimization based on  feature\mi /{MutiRes like wavelets}/{Intermodal}
\bibitem{Frame} Hong Shen, Charles V. Stewart, Badrinath Roysam, Gang Lin, and Howard L. Tanenbaum, "Frame-Rate Spatial Referencing Based on Invariant Indexing and Alignment with Application to On-Line Retinal Image Registration," IEEE Trans. on Pattern Analysis and Machine Intelligence, 2002.%feature-12-parameter quadratic/error norm
\bibitem{Curved} Ali Can, Charles V. Stewart, Badrinath Roysam, and Howard L. Tanenbaum, "A Feature-Based, Robust, Hierarichal Algorithm For Registering Pairs of Images of the Curved Human Retina," IEEE TRANSACTIONS ON PATTERN ANALYSIS AND MACHINE INTELLIGENCE, VOL. 24, NO. 3, MARCH 2002. %feature, 12-parameter quadratic/normalized sum of squared difference
\bibitem{Fusion} France Laliberté, Langis Gagnon, and Yunlong Sheng , "Registration and Fusion of Retinal Images$-$An Evaluation Study," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 22, NO. 5, MAY 2003.%feature-global point matching/(similarity, affine, and second-order polynomial)
\bibitem{Dual} Charles V. Stewart, Chia-Ling Tsai, and Badrinath Roys, "The Dual-Bootstrap Iterative Closest Point Algorithm With Application to Retinal Image Registration," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 22, NO. 11, NOVEMBER 2003.%feature/quadratic/covariance matrix {*}
%Intensity-Based 
\bibitem{Correlation2} WILLIAM K. PRATT, "Correlation Techniques of Image Registration," IEEE TRANSACTIONS ON AEROSPACE AND ELECTRONIC SYSTEMS, VOL. AES-10, NO. 3, MAY 1974.%area/corr
\bibitem{CorrelationRatio} A. Roche, G. Malandain, X. Pennec, N. Ayache, "The correlation ratio as a new similarity measure for multimodal image registration," Proceedings of the First International Conference on Medical Image Computing and Computer-Assisted Intervention (MICCAI'98), VOL. 1496, pp. 1115$-$1124, 1998.%not vascular/feature/corr ration, woods criterion/weighted neighbor likelihood/rigid {survey}
\bibitem{MultiMi1} Paul A. Viola, "Alignment by Maximization of Mutual Information," Proceedings of the 5th International Conference on Computer Vision, pages 15$-$23, 1995. %Intensity-based/Multimodal
\bibitem{MultiMi} Frederik Maes, Andr´e Collignon, Dirk Vandermeulen, Guy Marchal, and Paul Suetens, "Multimodality Image Registration by Maximization of Mutual Information," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 16, NO. 2, APRIL 1997.%non vascular/feature/applies MI to measure the statistical dependence or information redundancy between the image intensities/for rigid body registration{*}
\bibitem{Stereo} Nicola Ritter, Robyn Owens, James Cooper, Robert H. Eikelboom, and Paul P. van Saarloos, "Registration of Stereo and Temporal Images of the Retina," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 18, NO. 5, MAY 1999. %OD/Area-based, mi/simulated annealing with pyramid sampling
\bibitem{Likelihood} A. Roche, G. Malandain, N. Ayache, "Unifying maximum likelihood approaches in medical image registration," International Journal of Imaging Systems and Technology VOL. 11, pp. 71$-$80, 2000.%Correlation coefficient/correlation ratio, Mi /rigid transformation{survey}
\bibitem{2D3D2} Daniel B. Russakoff, Torsten Rohlfing, and Calvin R. Maurer, Jr.,  "Fast Intensity-based 2D-3D Image Registration of Clinical Data Using Light Fields", Proceedings of the Ninth IEEE International Conference on Computer Vision (ICCV'03), 2003.%Intensity-based/rigid/mi
\bibitem{Swarm} Mark P. Wachowiak, Renata Smolikova, Yufeng Zheng, Jacek M. Zurada, and Adel S. Elmaghraby, "An Approach to Multimodal Biomedical Image Registration Utilizing Particle Swarm Optimization," IEEE TRANSACTIONS ON EVOLUTIONARY COMPUTATION, VOL. 8, NO. 3, JUNE 2004. %non-vascular/feature/metric= normalized mutual information/optimizer= Particle Swarm Optimization
\bibitem{Correlation1} Jeongtae Kim and Jeffrey A. Fessler, "Intensity-Based Image Registration Using Robust Correlation Coefficients," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 23, NO. 11, NOVEMBER 2004.%area- proposed robust correlation similarity measure
\%bibitem{Phase3} Enrique Corona, Sunanda Mitra, and Mark Wilson, "A Fast Algorithm For Registration of Individual Frames and Information Recovery in Fluorescein Angiography Video Image Analysis," Fifth IEEE Southwest Symposium on Image Analysis and Interpretation," 2002. %not vascular/Feaure/affine%
%Intensity/Feature-Based
\bibitem{Landmark} H. J. Johnson, and G. E. Christensen, "Consistent Landmark and Intensity-Based Image Registration," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 21, NO. 5, MAY 2002.%not vascular/featue/TPS Model/combines feature and intensity/Area minimizing the inverse consistency error
\bibitem{Hybrid} Thitiporn Chanwimaluang, Guoliang Fan, and Stephen R. Fransen, "Hybrid Retinal Image Registration," IEEE TRANSACTIONS ON INFORMATION TECHNOLOGY IN BIOMEDICINE, VOL. 10, NO. 1, JANUARY 2006. %featue/Area  vasculature: local entropy thresholding technique/affine/quadratic/mi/ a local entropy-based peak selection and a multi-resolution searching schemes are developed to improve accuracy and efficiency of translation estimation
%----------------------
\bibitem{nonrigid} Lyubomir Zagorchev \& Ardeshir Goshtasby, "A Comparative Study of Transformation Functions for Nonrigid Image Registration," IEEE Trans. Image Processing, VOL. 15, NO. 3, pp. 529$-$538, 2006. %explores thin-plate spline (TPS), multiquadric (MQ), piecewise linear (PL), and weighted mean (WM) transformations{survey}

%\bibitem{k} F. Zana and J. C. Klein, "A multimodal registration algorithm of eye fundus images using vessels detection and Hough transform," IEEE Trans. Med. Imag., vol. 18, pp. 419$-$428, May 1999.
%matched filter
%drusen, morph
\bibitem{ii} Geir E. Oien, and Per Osnes, "Diabetic Retinopathy: Automatic Detection of early symptoms from retinal images," Proc. Norwegian Signal Processing Sym. 
%microaneurysm, morph
\bibitem{i} Meindert Niemeijer, Bram van Ginneken, Joes Staal, Maria S.A. Suttorp-Schulten, and Michael D. Abràmoff, "Automatic Detection of Red Lesions in Digital Color Fundus Photographs," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 24, NO. 5, MAY 2005.
\bibitem{j} C. I. O. Martins, F. N. S. Medeiros, R. M. S. Veras, F. N. Bezerra, and R. M. Cesar Jr., "EVALUATION OF RETINAL VESSEL SEGMENTATION METHODS FOR MICROANEURYSMS DETECTION," ICIP, 2009.
%optic disk localiation
\bibitem{h} Adam Hoover and Michael Goldbaum, "Locating the Optic Nerve in a Retinal Image Using the Fuzzy Convergence of the Blood Vessels," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 22, NO. 8, AUGUST 2003.
\bibitem{l} Aliaa Abdel-Haleim Abdel-Razik Youssif, Atef Zaki Ghalwash, and Amr Ahmed Sabry Abdel-Rahman Ghoneim, "Optic Disc Detection From Normalized Digital Fundus Images by Means of a Vessels' Direction Matched Filter," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 27, NO. 1, JANUARY 2008.
\bibitem{match1} S. Chaudhuri, S. Chatterjee, N. Katz, M. Nelson, and M. Goldbaum, "Detection of blood vessels in retinal images using two-dimensional matched filters," IEEE Trans. Med. Imag., vol. 8, pp. 263$-$269, Sept. 1989.
\bibitem{match2} L. Gang, O. Chutatape, and S. M. Krishnan, "Detection and measurement of retinal vessels in fundus images using amplitude modified second-order Gaussian filter," IEEE Trans. Biomed. Eng., vol. 49, pp. 168$-$172, Feb. 2002.
\bibitem{match3} Bob Zhang, Lin Zhang, Lei Zhang, and Fakhri Karray, "Retinal vessel extraction by matched filter with first-order derivative of Gaussian," Journal of Computers in Biology and Medicine, VOL. 40, pp. 438$-$445, 2010.
%thresholding
\bibitem{thresh} Adam Hoover, Valentina Kouznetsova, and Michael Goldbaum, "Locating Blood Vessels in Retinal Images by Piecewise Threshold Probing of a Matched Filter Response," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 19, NO. 3, MARCH 2000.
%ridge and edge grouping
\bibitem{ridge1} Joes Staal, Michael D. Abràmoff, Meindert Niemeijer, Max A. Viergever, and Bram van Ginneken, "Ridge-Based Vessel Segmentation in Color Images of the Retina," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 23, NO. 4, APRIL 2004.
%\bibitem{ridge2} Changhua Wu, Jennifer J. Kang Derwent, and Peter Stanchev, "Retinal Vessel Radius Estimation and a Vessel Center Line Segmentation Method Based on Ridge Descriptors," J Sign Process Syst, 2008.
\bibitem{groupp1} A. Pinz, S. Berngger, P. Datlinger, and A. Kruger, "Mapping the human retina," IEEE Trans. Med. Imag.m VOL. 17, pp. 606$-$619, Aug. 1998.
%tracking
\bibitem{track1} Yannis A. Tolias, and Stavros M. Panas, "A Fuzzy Vessel Tracking Algorithm for Retinal Images Based on Fuzzy Clustering", IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 17, NO. 2, APRIL 1998.
\bibitem{track2} O. Chutatape, L. Zheng, and S. M. Krishnan, "Retinal blood vessel detection and tracking by matched Gaussian and Kalman filters," in Proc. 20th Annu. Int. Conf. IEEE Eng. Med. Biol. Soc. (EMBS'98), 1998, vol. 20, pp. 3144$-$3149.
\bibitem{track3} A. Can, H. Shen, J. N. Turner, H. L. Tanenbaum, and B. Roysam, "Rapid automated tracing and feature extraction from retinal fundus images using direct exploratory algorithms," IEEE Trans. Inf. Technol. Biomed., vol. 3, no. 2, pp. 125$-$138, Jun. 1999.
\bibitem{track4} M. Lalonde, L. Gagnon, and M.-C. Boucher, "Non-recursive paired tracking for vessel extraction from retinal images," Vision Interface, pp. 61$-$68, 2000.
\bibitem{track5} Enrico Grisan, Alessandro Pesce, Alfredo Giani, Marco Foracchia, and Alfredo Ruggeri, "A new tracking system for the robust extraction of retinal vessel structure," Proceedings of the 26th Annual International Conference of the IEEE EMBS, 2004.
\bibitem{track6} Di Wu, Ming Zhang, Jyh-Charn Liu, and Wendall Bauman, "On the Adaptive Detection of Blood Vessels in Retinal Images, IEEE TRANSACTIONS ON BIOMEDICAL ENGINEERING," VOL. 53, NO. 2, FEBRUARY 2006.
\bibitem{track7} Farsad Zamani Boroujeni, Rahmita Wirza, Norwati Mustapha,Lilly Suriani Affendey,
Oteh Maskon and Majid Khalilian, "A New Tracing Algorithm for Automatic Boundary Extraction from Coronary Cineangiograms," Proceedings of The International MultiConference of Engineers and Computer Scientists, VOL. II, 2010.
%model-fitting
\bibitem{model} Vijay Mahadevan, Harihar Narasimha-Iyer, Badrinath Roysam, and Howard L. Tanenbaum, "Robust model-based vasculature detection in noisy biomedical imagings," IEEE TRANSACTIONS ON INFORMATION TECHNOLOGY IN BIOMEDICINE, VOL. 8, NO. 3, SEPTEMBER 2004.
%machine learning
\bibitem{machine1} Jao V. B. Soares, Jorge J. G. Leandro, Roberto M. Cesar Jr., Herbert F. Jelinek, and Michael J. Cree, Senior Member, IEEE, "Retinal Vessel Segmentation Using the 2-D Gabor Wavelet and Supervised Classification, IEEE TRANSACTIONS ON MEDICAL IMAGING," VOL. 25, NO. 9, SEPTEMBER 2006.
\bibitem{machine2} Lili Xu, Shuqian Luo, "A novel method for blood vessel detection from retinal images," BioMedical Engineering OnLine, 2010.
%mathematical morphology-unsupervised 
\bibitem{morph1} Frédéric Zana and Jean-Claude Klein, "Segmentation of Vessel-Like Patterns Using Mathematical Morphology and Curvature Evaluation," IEEE TRANSACTIONS ON IMAGE PROCESSING, VOL. 10, NO.7, JULY 2001.
\bibitem{morph2} Thomas Walter and Jean-Claude Klein, "Segmentation of Color Fundus Images of the Human Retina: Detection of the Optic Disc and the Vascular Tree Using Morphological Techniques," ISMDA 2001, LNCS 2199, pp. 282$-$287, 2001.
\bibitem{morph3} YONG YANG, SHUYING HUANG, and NINI RAO, "AN AUTOMATIC HYBRID METHOD FOR RETINAL BLOOD VESSEL EXTRACTION," Int. J. Appl. Math. Comput. Sci., Vol. 18, No. 3, 399$-$407, 2008.
\bibitem{morph4} Jian Chena, Jie Tiana, Zichun Tanga, Jian Xuea, Yakang Daia and Jian Zhenga, "Retinal vessel enhancement and extraction based on directional field," Journal of X-Ray Science and Technology, VOL. 16, pp. 189$-$201, 2008.
%region growing
\bibitem{region1} A. Vasilevskiy and K. Siddiqi, "Flux maximizing geometric flows," IEEE Trans. Pattern Anal. Mach. Intell., vol. 24, no. 12, pp. 1565$-$1578, Dec. 2002.
\bibitem{region2} Hao Ju-tao, and Zhao Jing-jing, "Shape Constraint Incorporated Geometric Flows for Blood Vessels Segmentation," International Conference on Computational Intelligence and Security, 2008.
%snakes
\bibitem{snake1} Tim McInerney, and Demetri Terzopoulos, "T-snakes: Topology adaptive snakes," Medical Image Analysis, VOL. 4, pp. 73$-$91, 2000.
\bibitem{snake2} Ricardo Toledo, Xavier Orriols, Xavier Binefa, Petia Radeva, Jordi Vitri`a, and J.J. Villanueva, "Tracking Elongated Structures using Statistical Snakes," IEEE Comput. Soc. Conf. Comput. Vision Pattern Recog. (CVPR), VOL. 1, 2000.
%vector fields
\bibitem{vector1} Benson Shu Yan Lam and Hong Yan, "A Novel Vessel Segmentation Algorithm for Pathological Retina Images Based on the Divergence of Vector Fields," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 27, NO. 2, FEBRUARY 2008.
%probabilistic filtering
\bibitem{prob} Changhua Wua and Gady Agamb, "Probabilistic Retinal Vessel Segmentation," SPIE Medical Imaging $-$ Image Processing (MI05), 2007.
\bibitem{prob2} Mouloud Adel, Monique Rasigni, Thierry Gaidon, Caroline Fossati, and Salah Bourennane, "STATISTICAL$-$BASED LINEAR VESSEL STRUCTURE DETECTION IN MEDICAL IMAGES," ICIP, 2009.
%matched filter, scale-space and region growing, morpolhogy, local thresholding, pixel classification
\bibitem{comp} M. Niemeijer, J. J. Staal, B. van Ginneken, M. Loog, and M. D. Abràmoff, "Comparative study of retinal vessel segmentation methods on a new publicly available database," in Proc. SPIE Med. Imag., J. M. Fitzpatrick and M. Sonka, Eds., vol. 5370, pp. 648$-$656, 2004.
%Fuzzy
\bibitem{a} Richard O. Duda, Peter E. Hart and David G. Stork 2003. Pattern Classificationm, Second Edition. Wiley-Interscience, USA.
\bibitem{b} Ethem Alpaydm. Introduction to Machine Learning. The MIT Press, Cambridge, England. 

%Camera
\bibitem{cam1} Oleg Pomerantzeff, Robert H. Webb, and Francois C. Delori, "Image formation in fundus cameras," Assoc. for Res. in Vis. and Ophthal., Inc., Aug. 14, 1978.
\bibitem{cam2} Patrick J. Saine, "Errors in Fundus Photography," Journal of Ophthalmic Photography, Vol. 7, No. 2, December 1984.
\bibitem{cam3} Edward DeHoog and James Schwiegerling, "Fundus camera systems: a comparative analysis," Appl Opt., VOL. 48, NO. 2, pp. 221$-$228, January 2009.
%\bibitem{cam6} Eli Peli, and Tamar Peli, "Restoration of Retinal Images Obtained Through Cataracts," IEEE TRANSACTIONS ON MEDICAL IMAGING, VOL. 8, NO. 4, DECEMBER 1989.  
%\bibitem{cam4} Michael J Cree, John A Olson, Kenneth C McHardy, Peter F Sharp and John V Forrester, "The preprocessing of retinal images for the detection of fluorescein leakage," Phys. Med. Biol., VOL. 44, pp. 293$-$308, 1999.
%\bibitem{cam5} J. Liu, S. Lu, J.H. Lim, Z. Zhang, T.N. Meng, D.W.K. Wong, and H. Li, and T.Y. Wong, "PHOTOMETRIC CORRECTION OF RETINAL IMAGES BY POLYNOMIAL INTERPOLATION," ICIP, 2009.

\bibitem{gl} R. Theodore Smith, Jackie K. Chan, Takayuki Nagasaki, Umer F. Ahmad, Irene Barbazetto, Janet Sparrow, Marta Figueroa, and Joanna Merriam, "Automated Detection of Macular Drusen Using Geometric Background Leveling and Threshold Selection," ARCH OPHTHALMOL, vol. 123, 2005.
\bibitem{d} R. Theodore Smith, Jan P. Koniarek, Jackie Chan, Takayuki Nagasaki, Janet R. Sparrow, and Kevin Langton, "Autofluorescence Characteristics of Normal Foveas and Reconstruction of Foveal Autofluorescence from Limited Data Subsets," Investigative Ophthalmology \& Visual Science, Vol. 46, No. 8, 2005.

\bibitem{em} A. P. Dempster, N. M. Laird, and D. B. Rubin, "Maximum likelihood from incomplete data via the EM algorithm," Journal Royal Statistics Society, vol. 39, no. 1, pp. 1-21, 1977.
 Taban M, Sharma S, Williams DR, Waheed N, and Kaiser PK, "Comparing retinal thickness measurements using automated fast macular thickness map versus six-radial line scans with manual measurements," Ophthalmology, vol. 116, no. 8, pp. 964-70, May 2009.

\bibitem{Alnagdawi2013}

\end{thebibliography}

%\newpage
%\begin{subappendices}
%
%\section{Appendix A}\label{A}
%Please refer to Appendix \ref{C}.
%
%\section{Second appendix}\label{B}
%Please refer to Appendix \ref{A}.
%
%\section{Third appendix}\label{C}
%Please refer to Appendix \ref{B}.
%
%\end{subappendices}
\newpage
