
\addcontentsline{toc}{chapter}{Dedication}
%\cchapter*{\textit{\LARGE{\mdseries{Dedication}}}}

%\textit{\\To all my family members, especially my mum and dad, to my predestined and future life mate to be by gods will, and to all my lovely friends, who supported me and have always stood by my side through all times.}

\newpage
\addcontentsline{toc}{chapter}{Acknowledgment}
\cchapter*{\LARGE{\mdseries{\uppercase{Acknowledgment}}}}

First and foremost, I would like to thank God for giving me the strength, knowledge, ability and opportunity to undertake this research study and to persevere and complete it satisfactorily. Without His blessings, this achievement would not have been possible. 

I would first like to thank my family,especially Mom, whose dream was to see me achieve this degree -God bless her- and Dad, for the continuous support they have given me throughout my studies; I could not have done it without them. Second, I would like to thank my wife Kholoud for all the love, comfort, and encouragement which motivated me to complete this thesis and my master’s studies at Nile University. 

I would like to thank my supervisor, Associate Professor Waleed A. Yousef, for introducing me to the field of machine learning and guiding me patiently throughout my undergraduate studies and MSc. studies. I am grateful for being given the chance to be part of the Informatics group and to collaborate with such brilliant researchers at Nile University.

I thank the members of my committee, Professors Samhaa El-Beltagy, Mohsen Rashwan, and Nashwa Abdelbaki, for their valuable time and ideas to enhance this research work. 

I thank all my co-authors, without whom this work would not have been possible, especially Taha M. Madbouly and Omar M. Ibrahime for all their hard work and their dedication to complete this work. 

I thank Mohamed Al-Aggan for his valuable insights in my research. Thanks also to Mohamed Abdel Aziz who helped me during our study in NU. I have met many great people during my studies. To name a couple of my professors who greatly affected my career, I would like to thank Dr.Ayman Ezzat and, Dr.Sameh Al-Ansari. I also need to thank two of my friends who helped me a lot and mentor me: Deyaaeldeen Al-Mahallawi and Omar Marzouk.


%I would like to acknowledge and express my heartfelt gratitude to the persons who have made the achievement of my Master of Science degree possible: \\\\
%Dr. Ahmed Samir Fahmy, for his outstanding assistance and guidance, encouragement, and support all the way.\\\\
%Dr. Ahmed El-Antably, Dr. Nermin Fawzy, and Dr. Mustafa Hunter for their great share and effort in this research.\\\\
%All the Nile University Faculty Members and Staff. \\\\
%Most especially to my family for their help and patience.\\\\
%And above all to God, who have made all things possible.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../master"
%%% TeX-engine: xetex
%%% End:
